\documentclass[12pt]{article}
\usepackage{fullpage, amssymb,amsmath}
\pagestyle{empty}
\input{../macros}
\begin{document}
{\bf STA721  }
\vspace{.1in}
\begin{center}
{\large \bf Homework 12} \\
\end{center}
\vspace{.5in}
\noindent

\begin{enumerate}

\item Consider the model: $$\Y = \X_0 \b_0 + \X_1 \b_1 + \eps$$
where under $H_a:  \mub \in C(\X_0, \X_1)$  where the number of
parameters is $p$.  (Assume everything is full rank).
To test that $\b_1 = \zero_q$,
the F statistic
$$F =  \frac{\| (\P_{\X_0,\X_1} - \P_{\X_0} )\Y \|^2 /q) }
{\hat{\sigma}^2} \sim F( q,  n - p)$$
under the null hypothesis $H_o: \mub \in C(\X_0)$ and $\hat{\sigma}^2$ is
the MSE from the full model  $H_a$.

\begin{enumerate}
\item Show that $\P_{\X_0,\X_1} - \P_{\X_0}$ is a projection and
  describe the space onto which it projects.
\item Show that the numerator and denominator are independent and find
  the respective distributions of the two quadratic forms.
\item Find the expected value of the numerator under $H_0$ and $H_a$ (simplify
  as much as possible).   Do you expect the numerator to be larger
  than $\sigma^2$ if the alternative hypothesis is true?
\item Find the expected value of $\hat{\sigma}^2$ under $H_o$ and
  $H_a$.
\item If we instead use the estimate of $\sigma^2$ from the null
  model,  is that an unbiased estimate of $\sigma^2$ under $H_0$?
  under $H_a$?  Explain why it is preferable to use the estimate from
  the largest model. 

\end{enumerate}

\item Apply lasso and horseshoe to the Climate Change data (you will
  have to pick a basis/design matrix).  What can they tell you about
  the questions of interest?  If you code the dummy variables or
  polynomials in latitude differently will this result in different
  conclusions? (Explore). Do they provide measures of uncertainty
  about the degree of temperature changes?   Write a
  brief summary of your analysis and recommendation.
 
\end{enumerate}
\end{document}